---
title: "p8105_hw1_yz4187"
author: Yiwen Zhao
date: 2021-09-27
output: github_document
    
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

### Problem 1

This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

```{r}
learning_df = 
  tibble(
    sample = rnorm(10),
    gr_than_0 = sample > 0,
    vec_char = c("a","b","c","d","e","f","g","h","i","j"),
    vec_factor = factor(c("1","2","3","1","2","3","1","2","3","1"))
  )



mean(pull(learning_df, var = 1))
mean(pull(learning_df, var = 2))
mean(pull(learning_df, var = 3))
mean(pull(learning_df, var = 4))
```
* The means of "sample" and "gr_than_0" can work, but the means for "vec_char" and "vec_factor" can not work.
```{r, eval= FALSE}
as.numeric(levels(learning_df))
```
* According to the as.numeric function, we can see that the mean for colume "vec_char" and "vec_fator" are "N/A" since they are not numbers. The as.numeric function helps to show which colume is not able to transfer to numeric. Since these two columes are not numbers, we can not get the means.


### Problem 2
```{r, warning=FALSE}
data("penguins", package = "palmerpenguins")

names(penguins)
nrow(penguins)
ncol(penguins)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("results/scatter_plot.pdf")
```



